Unveiling Exception Handling Bug Hazards in Android based on GitHub and Google Code Issues

### 2015-02-16 android-stacks.tex
Conclusions done.
Rewrite to make sure that we list the contributions and key
findings.

In this paper we present an exploratory study in which we mined the stack 
traces embedded in all issues defined in 482 Android projects hosted in Github and 
157 projects hosted in Google Code. Overall it included 6,005 exception stack traces.
In this study, the information extracted from stack traces was used in combination 
with source code and bytecode analysis to identify common characteristics of exception 
stack traces to pinpoint \emph{bug hazards} on the exception-related code. 
In this study, \emph{bug hazards} are characteristics on the exception-related code that favor the introduction
of  uncaught exceptions and unintended handling - which can contribute to 
degrade the robustness of applications.
Some \emph{bug hazards} consistently detected in this study were: 
(i) unexpected exception wrappings (e.g., Errors being wrapped in checked exceptions)  - 
revealing that Java hybrid exception model is not fully used according to its purpose;
(ii) 267 stack traces were caused by undocumented runtime exceptions thrown by third party libraries or the Android Platform;
and (iii) undocumented checked exceptions thrown by the Android Platform. 
Moreover, we could also observe that approximately 52\% of the reported stack traces 
can be attributed to programming mistakes; in particular, 27.71\% of all stack traces 
reported a java.lang.NullPointerException as its root cause;
The \emph{bug hazards} discussed in this work can negatively affect not only the robustness of Android application 
but also the robustness of any Java-based application. 
Our results calls the attention for the need of tools and language support to help 
developers when dealing with them.

>>>>

The goal of this paper is to investigate 
to what extent stack trace information can reveal \emph{bug hazards} 
related to exception handling code that may lead to a decrease in
application robustness. 
To that end, we mined the stack 
traces embedded in all issues defined in 482 Android projects hosted in Github and 
157 projects hosted in Google Code. Overall it included 6,005
exception stack traces.

Our first key contribution is
a novel approach and toolset (ExceptionMiner) for analyzing Java
  exception stack traces as occurring on GitHub and Google Code
  issues.
Our second contribution is
an empirical study of over 6000 actual stack traces,
  demonstrating that (1) half of the system crashes are due to errors
  in programming logic, with null pointer exceptions being most
  prominent;
  (2) Documentation for explicitly thrown RuntimeExceptions is almost
  never provided; 
  (3) Extensive use of wrapping leads to hard to understand chains
  violating Java's exception handling principles.

Our results shed light on common problems and bug hazards in Java
exception handling code, and call for tool support to help developers
understand their own and third party exception handling and wrapping logic.
